### 2020-10-15 introduction.tex
important contribution
Update introduction.tex

We make the following contributions:
\begin{itemize}
\item \emph{Priority GV} We present Priority GV (PGV) in~\cref{sec:pgv}, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}).
\item \emph{Milner's Cyclic Scheduler} To illustrate newfound expressiveness of PGV, we present Milner's Cyclic Scheduler~\cite{milner89} (\cref{sec:pgv-example}).
\item \emph{Updated Priority CP} We present an updated version of Priority CP (PCP)~\cite{dardhagay18} in \cref{sec:pcp}. We remove commuting conversions and move away from reduction as cut elimination, towards reduction based on structural congruence, as one expects in a process calculus. We present Milner's Cyclic Scheduler in PCP (\cref{sec:pcp-example}).
\item \emph{Translation from PCP to PGV} We present a translation from PCP in PGV in~\cref{sec:pcp}. We prove the translation preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}), and show that the scheduler in PCP (\cref{sec:pcp-example}) translates to the scheduler in PGV (\cref{sec:pgv-example}).
\end{itemize}
\end{document}

>>>>

We make the following contributions:
\begin{itemize}
\item \emph{Priority GV} We present Priority GV (PGV) in~\cref{sec:pgv}, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}). Unlike  previous work on GV, structural congruence and reduction are type preserving in PGV.
\item \emph{Milner's Cyclic Scheduler} To illustrate newfound expressiveness of PGV, we present Milner's Cyclic Scheduler~\cite{milner89} (\cref{sec:pgv-example}).
\item \emph{Updated Priority CP} We present an updated version of Priority CP (PCP)~\cite{dardhagay18} in \cref{sec:pcp}. We remove commuting conversions and move away from reduction as cut elimination, towards reduction based on structural congruence, as one expects in a process calculus. We present Milner's Cyclic Scheduler in PCP (\cref{sec:pcp-example}).
\item \emph{Translation from PCP to PGV} We present a translation from PCP to PGV in~\cref{sec:pcp} and prove that it preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}). We show that the scheduler in PCP (\cref{sec:pcp-example}) translates to the scheduler in PGV (\cref{sec:pgv-example}).
\end{itemize}
\end{document}
